Interactive Filter and Display of Hillary Clinton's Emails: \\A Cautionary Tale of Metadata

### 2017-03-23 VAST_submission/vgtc_journal_latex/paper.tex
Updated teaser

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \includegraphics[width=\linewidth]{SpiralNetworkOctNov2012}
  \caption{In the Clouds: Vancouver from Cypress Mountain. Note that the teaser may not be wider than the abstract block.}
	\label{fig:teaser}
}

>>>>

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \begin{tabular}{cc}
  \includegraphics[width=0.25\textheight]{DailySept11ToNov152012_All} &
  \includegraphics[width=0.25\textheight]{InnerCircleSept11ToNov152012_All} \\
  &\\
  {\small (a) Missing data in November.} & {\small (b) Inner Circle: Correspondent info by colour; volume by thickness.}
  \end{tabular}
  \caption{Metadata: Time, date, correspondents, volume.  Filtered: Sept. 11 to Nov. 15, 2012.  
  %Source: \href{https://wikileaks.org/clinton-emails/}{\texttt{https://wikileaks.org/clinton-emails/}}
  }

	\label{fig:teaser}
}
